Comparing human and model-based forecasts of COVID-19 in Germany and Poland

### 2021-10-13 manuscript/manuscript.Rmd
add citations

Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza [CITATION], dengue fever [Citation], ebola [Citation], chikungunya and now COVID-19 [Citation]. The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models (CITE e.g UK, US and German/Polish papers). Yet it has been difficult to discern which factors lead to good COVID-19 forecasts. Answering this question is complicated by the varying and generally unobserved degree of manual expert intervention. Model-based forecasts usually represent an implicit combination of human judgement and model-derived insights, in the sense that forecasts have been generated with the help of epidemiological or statistical models, but throughout the process were manually changed and adjusted according to the researchers’ judgement.

Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al. 2014; Atanasov et al. 2016), meta-science (Cite Replication Markets), and epidemiology (CITE FARROW ET AL, McAndrew et al. 2021, Cite that other paper). Several prediction platforms (Metaculus 2020, Hypermind, Foretell) and prediction markets (cite predictit) have been created to collate expert and non-expert predictions. However, with the notable exception of Farrow et al., these crowd forecasts  were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats. Farrow et al. found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available. They tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.

In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts and model-based predictions.

@@

We created a crowd-sourced forecast (“crowd forecast”), elicited from participants through a web application [Citation], as well as two semi-mechanistic models ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology. Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub (CITATION). All code and tools necessary to generate the forecasts and make a forecast submission are available in the `covid.german.forecasts` R package (N. Bosse et al. 2020). This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub. Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the Forecast Hub.

@@

Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub (J. Bracher et al. 2021). Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) (“Download Historical Data (to 14 December 2020) on the Daily Number of New Reported COVID-19 Cases and Deaths Worldwide” 2020). After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period (“RKI - Coronavirus SARS-CoV-2 - Aktueller Lage-/Situationsbericht Des RKI Zu COVID-19” n.d.). These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November (“Rozbieżności w statystykach koronawirusa. 22 tys. przypadków będą doliczone do ogólnej liczby wyników” 16:07:56+0100)), changes in reporting over time and variation in testing regimes (e.g. in Germany from the 11th of November on (Ärzteblatt 2020)).

@@

Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application  (https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday. The application was built using the shiny and golem R packages (Chang et al. 2021; Fay et al. 2021) and is available in the crowdforecastr R package (N. I. Bosse et al. 2020). To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values. The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e. as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`). 
Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from (“COVID-19 Data Explorer” n.d.). These data included e.g. notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.

@@

We used two models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts (Abbott, Hellewell, et al. 2020). The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths. It estimated the effective reproduction number $R_t$ (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times $R_t$. $R_t$ was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in infections. The $R_t$ value which was carried forward was slightly changed on November 9th 2020, where before that date the last 'reliable' $R_t$ estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) $R_t$ estimate made on the actual forecast date was used. Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions (Abbott, Hellewell, et al. 2020; DOI n.d.; “Evaluating the Use of the Reproduction Number as an Epidemiological Tool, Using Spatio-Temporal Trends of the Covid-19 Outbreak in England | medRxiv” n.d.) to model the time between infection and report date or death. The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that $R_t$ was forecast once from reported cases and once from reported deaths. Death forecasts from the renewal model were therefore not informed by past cases. One submission of the renewal model on December 28th 2020 was belated and therefore not included in the official Forecast hub ensemble.

The second model (“convolution model”) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses). The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model. The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio). Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect (Abbott, Hellewell, et al. 2020). Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from (Xu et al., n.d.) with data available up to the 1st of August. All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan (Stan Development Team 2020) with each location and forecast target being fit separately. More details are available in the supplementary information.

@@

Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher et al. 2021), the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals. The WIS is a proper scoring rule (CITE GNEITING) and can be understood as a generalisation of the absolute error to quantile-based forecasts. It can be decomposed into three separate penalties: forecast spread (i.e. uncertainty of forecasts), over-prediction and under-prediction - lower values are always better. While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts. The bias metric we use captures how much probability mass of the forecast was above or below the true value and therefore represents a general tendency to over- or under-predict in relative terms. It is bound between -1 (all quantiles of the predictive distribution are below the observed value) and 1 (all quantiles are above the observed value). Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g. how many observed values fall inside all 50% prediction intervals). Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI. All scores were calculated using the `scoringutils` R package (N. Bosse 2020).

@@

Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts. However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches (Cite US Hub, cite Seb SPI-M), or exclusively on human forecasts (e.g. cite Tetlock, cite Grecchia, cite McAndrew). In contrast, we directly compared human and model-based forecasts. This is similar to the approach taken by Farrow et al., but extends it in several ways. While Farrow et al. only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence. In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight. In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (J. Bracher et al. 2021; E. Y. Cramer et al. 2021; S. Funk et al. 2020).

@@

where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above. This adjustment is based on that implemented in the `epidemia` R package (@epidemia, cite @bhatt202).

>>>>

Infectious disease forecasting has a long tradition and has helped inform public health decisions about (among others) influenza [e.g. @mcgowanCollaborativeEffortsForecast2019; @reichCollaborativeMultiyearMultimodel2019; @shamanForecastingSeasonalOutbreaks2012; @biggerstaffResultsCentersDisease2016], dengue fever [e.g. @johanssonOpenChallengeAdvance2019; @yamanaSuperensembleForecastsDengue2016; @colon-gonzalezProbabilisticSeasonalDengue2021], ebola [e.g. @viboudRAPIDDEbolaForecasting2018; @funkAssessingPerformanceRealtime2019], chikungunya [e.g. @delvalleSummaryResults201420152018; @farrowHumanJudgmentApproach2017] and now COVID-19 [e.g. @funkShorttermForecastsInform2020; @esteecramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021; @bracherShorttermForecastingCOVID192021; @EuroHub]. The aggregation of forecasts of COVID-19 cases, hospitalisations or deaths from multiple teams has created opportunities to compare the predictive performance of different models. Yet it has been difficult to discern which factors lead to good COVID-19 forecasts. Answering this question is complicated by the varying and generally unobserved degree of manual expert intervention. Model-based forecasts usually represent an implicit combination of human judgement and model-derived insights, in the sense that forecasts have been generated with the help of epidemiological or statistical models, but throughout the process were manually changed and adjusted according to the researchers’ judgement.

Previous work has examined human predictions in various contexts, such as geopolitics [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016], meta-science [@hoogeveenLaypeopleCanPredict2020; @ReplicationMarketsReliable], sports [@servan-schreiberPredictionMarketsDoes2004] and epidemiology [@farrowHumanJudgmentApproach2017; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021]. Several prediction platforms [@metaculusPreliminaryLookMetaculus2020; @HypermindSupercollectiveIntelligence; @CSETForetell] and prediction markets [@Predictit] have been created to collate expert and non-expert predictions. However, with the notable exception of Farrow et al., these crowd forecasts  were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats. Farrow et al. found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available. They tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.

In this study, we attempt to further shed light on the role of human judgement and model-derived insight and analyse respective strengths and weaknesses by comparing human forecasts with a full predictive distribution and model-based predictions.

@@

We created a crowd-sourced forecast (“crowd forecast”), elicited from participants through a web application [@crowdforecastr], as well as two semi-mechanistic models ("renewal model" and "convolution model") informed by basic assumptions about COVID-19 epidemiology. Forecasts were created in real time over a period of 21 weeks from October 12th 2020 until March 1st 2021 and submitted to the German and Polish Forecast hub [@bracherShorttermForecastingCOVID192021]. All code and tools necessary to generate the forecasts and make a forecast submission are available in the `covid.german.forecasts` R package [@covidgermanforecasts]. This repository also contains a record of all forecasts submitted to the German and Polish Forecast Hub. Forecasts were evaluated using a variety of scoring metrics and compared among each other and against an ensemble of all other models submitted to the Forecast Hub.

@@

Data on daily reported test positive cases and deaths linked to Covid-19 were provided by the organisers of the German and Polish forecast hub (J. Bracher et al. 2021). Until December 14th 2020 these data were sourced from the European Centre for Disease Control (ECDC) [@DownloadHistoricalData2020a]. After ECDC stopped publishing daily data, observations were sourced from the Robert Koch Institute (RKI) and the Polish Ministry of Health for the remainder of the submission period  [@RKICoronavirusSARSCoV2a]. These data are subject to reporting artefacts (such as a delayed case reporting in Poland on the 24th November [@RozbieznosciStatystykachKoronawirusa0100]), changes in reporting over time and variation in testing regimes (e.g. in Germany from the 11th of November on [@aerzteblattSARSCoV2DiagnostikRKIPasst2020]).

@@

Our crowd forecasts were created as an ensemble of forecasts made by individual participants every week through a web application  (https://cmmid-lshtm.shinyapps.io/crowd-forecast/). Forecasts were allowed until 12pm on Tuesdays, but participants were asked to only use information available until Monday. The application was built using the shiny and golem R packages [@golem; @shiny] and is available in the `crowdforecastr` R package [@crowdforecastr]. To make a forecast in the application participants could select a predictive distribution, with the default being log-normal, and adjust the median and the width of the uncertainty by either interacting with a figure showing their forecast or providing numerical values. The baseline shown was a repetition of the last known observation with constant uncertainty around it computed as the standard deviation of the last four changes in log observed forecasts (i.e. as `sd(c(log(value4) - log(value3), log(value3) - log(value2), ...))`). 
Our interface also allowed participants to view the observed data, and their forecasts, on a logarithmic scale and presented additional contextual COVID-19 data sourced from  [@COVID19DataExplorer]. These data included e.g. notifications of both test positive COVID-19 cases and COVID-19 linked deaths and the number of COVID-19 tests conducted over time.

@@

We used two models from the `EpiNow2` R package (version 1.3.3) as our model-based forecasts [@epinow2]. The first of these models, here called “renewal model”, used the renewal equation [@fraserEstimatingIndividualHousehold2007] to predict reported cases and deaths. It estimated the effective reproduction number $R_t$ (the average number of people each infected person is expected to infect in turn) and models future infections as a weighted sum of past infections times $R_t$. $R_t$ was assumed to stay constant in the future, roughly corresponding to continuing the latest trend in infections. The $R_t$ value which was carried forward was slightly changed on November 9th 2020, where before that date the last 'reliable' $R_t$ estimate from X days before the forecast was used and after that the latest and most up-to-date (but possibly less stable) $R_t$ estimate made on the actual forecast date was used. Reported cases and deaths were obtained by convolving predicted infections over data-based delay distributions [@epinow2; @doiCovid19TemporalVariation; @EvaluatingUseReproduction] to model the time between infection and report date or death. The renewal model was used to predict cases as well as deaths, but the two were forecast completely independently, meaning that $R_t$ was forecast once from reported cases and once from reported deaths. Death forecasts from the renewal model were therefore not informed by past cases. One submission of the renewal model on December 28th 2020 was belated and therefore not included in the official Forecast hub ensemble.

The second model (“convolution model”) was only used to forecast deaths and was added later, starting December 7th 2020 (with the first forecast from December 7th suffering from a software bug and therefore disregarded in all further analyses). The convolution model was submitted, but never included in the official Forecast hub ensemble due to concerns that it could be too similar to the renewal model. The convolution model predicted deaths these as a fraction of infected people who would die with some delay, by using a convolution of reported cases with a distribution that described the delay from case report to death and a scaling factor (the case-fatality ratio). Both the renewal and the convolution model used daily observations and assumed a negative binomial observation model and a multiplicative day-of-the-week effect [@epinow2]. Line list data used to inform the delay from symptom onset to test positive case report or death in the model-based forecasts was sourced from [@kraemer2020epidemiological] with data available up to the 1st of August. All model fitting was done using Markov-chain Monte Carlo (MCMC) in stan  [@rstan]  with each location and forecast target being fit separately. More details are available in the supplementary information.

@@

Forecasts were analysed using the following scoring metrics: The weighted interval score (WIS) (Johannes Bracher et al. 2021), the absolute error, relative bias, and empirical coverage of the 50% and 90% prediction intervals. The WIS is a proper scoring rule [@gneiting_strictly_2007] and can be understood as a generalisation of the absolute error to quantile-based forecasts. It can be decomposed into three separate penalties: forecast spread (i.e. uncertainty of forecasts), over-prediction and under-prediction - lower values are always better. While the over- and under-prediction components of the WIS capture the amount of over-prediction and under-prediction in absolute terms, we also look at a relative tendency to make biased forecasts. The bias metric we use captures how much probability mass of the forecast was above or below the true value and therefore represents a general tendency to over- or under-predict in relative terms. It is bound between -1 (all quantiles of the predictive distribution are below the observed value) and 1 (all quantiles are above the observed value). Empirical coverage is the percentage of observed values that fall inside a given prediction interval (e.g. how many observed values fall inside all 50% prediction intervals). Scoring metrics are explained in more detail in Table \@ref(tab:scoring-metrics) in the SI. All scores were calculated using the `scoringutils` R package (N. Bosse 2020).

@@

Past studies have evaluated the performance of model-based forecasting approaches as well as human experts and non-experts in various contexts. However, most of these studies either focused only on the evaluation of (expert-tuned) model-based approaches [e.g. @funkShorttermForecastsInform2020; @esteecramerCOVID19ForecastHub2020; @cramerEvaluationIndividualEnsemble2021], or exclusively on human forecasts [@tetlockForecastingTournamentsTools2014; @atanasovDistillingWisdomCrowds2016; @mcandrewExpertJudgmentModel2020, @recchiaHowWellDid2021]. In contrast, we directly compared human and model-based forecasts. This is similar to the approach taken by @farrowHumanJudgmentApproach2017, but extends it in several ways. While Farrow et al. only asked for point predictions and constructed a probabilistic forecast from these, we asked participants to quantify their uncertainty directly, allowing us to compare human forecasts and models without any further assumptions, as well as to analyse aspects of the forecasts like overconfidence. In addition, we compared crowd forecasts to two semi-mechanistic models informed by basic epidemiological knowledge of COVID-19, allowing us to assess not only relative performance but also to analyse qualitative differences between human judgement and model-derived insight. In terms of interpretability of the results, exact knowledge of our two models, as well as focus on a limited set of targets and locations was a major advantage of our study compared to larger studies conducted by the Forecast Hubs (J. Bracher et al. 2021; E. Y. Cramer et al. 2021; S. Funk et al. 2020).

@@

where $I^c_t = \sum_{s< t} I_s$ are cumulative infections by $t-1$ and $I'_t$ are the unadjusted infections defined above. This adjustment is based on that implemented in the `epidemia` R package [@epidemia; @bhatt202].

### 2021-10-13 manuscript/manuscript.tex
add citations

Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al.~2014; Atanasov et al.~2016), meta-science (Cite Replication Markets), and epidemiology (CITE FARROW ET AL, McAndrew et al.~2021, Cite that other paper). Several prediction platforms (Metaculus 2020, Hypermind, Foretell) and prediction markets (cite predictit) have been created to collate expert and non-expert predictions. However, with the notable exception of Farrow et al., these crowd forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats. Farrow et al.~found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available. They tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.

@@

@@

@@

@@

@@

@@

>>>>

Previous work has examined human predictions in various contexts, such as geopolitics (Tetlock et al. 2014; Atanasov et al. 2016), meta-science (Hoogeveen, Sarafoglou, and Wagenmakers 2020; {``Replication {Markets} -- {Reliable} Research Replicates\ldots you Can Bet on It.''} n.d.), sports (Servan-Schreiber et al. 2004) and epidemiology Recchia, Freeman, and Spiegelhalter (2021). Several prediction platforms (Metaculus 2020; {``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers''} n.d.; {``{CSET Foretell}''} n.d.) and prediction markets (\textbf{Predictit?}) have been created to collate expert and non-expert predictions. However, with the notable exception of Farrow et al., these crowd forecasts were not designed to be evaluated alongside model-based forecasts and usually follow their own (often binary) formats. Farrow et al.~found that humans could outperform computer models at predicting the 2014/15 and 2015/16 flu season in the US, a setting where the disease was well known and information about previous seasons was available. They tended to do slightly worse at predicting the 2014/15 outbreak of chikungunya in the Americas, a disease previously largely unobserved and unknown there and then.

@@

\leavevmode\vadjust pre{\hypertarget{ref-atanasovDistillingWisdomCrowds2016}{}}%
Atanasov, Pavel, Phillip Rescober, Eric Stone, Samuel A. Swift, Emile Servan-Schreiber, Philip Tetlock, Lyle Ungar, and Barbara Mellers. 2016. {``Distilling the {Wisdom} of {Crowds}: Prediction {Markets} Vs. {Prediction Polls}.''} \emph{Management Science} 63 (3): 691--706. \url{https://doi.org/10.1287/mnsc.2015.2374}.

\leavevmode\vadjust pre{\hypertarget{ref-CSETForetell}{}}%
{``{CSET Foretell}.''} n.d. Accessed October 13, 2021. \url{https://www.cset-foretell.com/}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-farrowHumanJudgmentApproach2017}{}}%
Farrow, David C., Logan C. Brooks, Sangwon Hyun, Ryan J. Tibshirani, Donald S. Burke, and Roni Rosenfeld. 2017. {``A Human Judgment Approach to Epidemiological Forecasting.''} \emph{PLOS Computational Biology} 13 (3): e1005248. \url{https://doi.org/10.1371/journal.pcbi.1005248}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-hoogeveenLaypeopleCanPredict2020}{}}%
Hoogeveen, Suzanne, Alexandra Sarafoglou, and Eric-Jan Wagenmakers. 2020. {``Laypeople {Can Predict Which Social}-{Science Studies Will Be Replicated Successfully}.''} \emph{Advances in Methods and Practices in Psychological Science} 3 (3): 267--85. \url{https://doi.org/10.1177/2515245920919667}.

\leavevmode\vadjust pre{\hypertarget{ref-HypermindSupercollectiveIntelligence}{}}%
{``Hypermind \textbar{} {Supercollective} Intelligence for Decision Makers.''} n.d. {Hypermind}. Accessed October 13, 2021. \url{https://www.hypermind.com/en/}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-mcandrewExpertJudgmentModel2020}{}}%
McAndrew, Thomas Charles, and Nicholas G. Reich. 2020. {``An Expert Judgment Model to Predict Early Stages of the {COVID}-19 Outbreak in the {United States}.''} \emph{medRxiv}, September, 2020.09.21.20196725. \url{https://doi.org/10.1101/2020.09.21.20196725}.

\leavevmode\vadjust pre{\hypertarget{ref-metaculusPreliminaryLookMetaculus2020}{}}%
Metaculus. 2020. {``A {Preliminary Look} at {Metaculus} and {Expert Forecasts}.''} June 22, 2020. \url{https://www.metaculus.com/news/2020/06/02/LRT/}.

\leavevmode\vadjust pre{\hypertarget{ref-recchiaHowWellDid2021}{}}%
Recchia, Gabriel, Alexandra L. J. Freeman, and David Spiegelhalter. 2021. {``How Well Did Experts and Laypeople Forecast the Size of the {COVID}-19 Pandemic?''} \emph{PLOS ONE} 16 (5): e0250935. \url{https://doi.org/10.1371/journal.pone.0250935}.

\leavevmode\vadjust pre{\hypertarget{ref-ReplicationMarketsReliable}{}}%
{``Replication {Markets} -- {Reliable} Research Replicates\ldots you Can Bet on It.''} n.d. Accessed October 13, 2021. \url{https://www.replicationmarkets.com/}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-servan-schreiberPredictionMarketsDoes2004}{}}%
Servan-Schreiber, Emile, Justin Wolfers, David M. Pennock, and Brian Galebach. 2004. {``Prediction {Markets}: Does {Money Matter}?''} \emph{Electronic Markets} 14 (3): 243--51. \url{https://doi.org/10.1080/1019678042000245254}.

@@

\leavevmode\vadjust pre{\hypertarget{ref-tetlockForecastingTournamentsTools2014}{}}%
Tetlock, Philip E., Barbara A. Mellers, Nick Rohrbaugh, and Eva Chen. 2014. {``Forecasting {Tournaments}: Tools for {Increasing Transparency} and {Improving} the {Quality} of {Debate}.''} \emph{Current Directions in Psychological Science} 23 (4): 290--95. \url{https://doi.org/10.1177/0963721414534257}.
